Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-26 prob.tex
prob.tex \section{Proof} Keep typing...

\begin{definition}[Quantum Probability Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
Given a Hilbert space $\Hilb$ with its set of events~$\events$,
a \emph{quantum probability measure} is a function~$\mu:\events\rightarrow[0,1]$
such that:\footnote{It is possible to define a more general space of events consisting
of all operators~$\mathcal{A}$ on $\Hilb$ and to extend $\mu$
linearly to $\mathcal{A}$ and consider $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$
is the expectation value of $A$ which could bigger than one because
$\mu$ is linear. We does not take this approach because we want to
focus only on probability. } 
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, 
\begin{equation}
\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)\textrm{ .}\label{eq:QuantumReal-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=0}^{N-1}$,
we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{N-1}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\mu\left(P_{i}\right)$
. 
\end{itemize}
\qed\end{definition}

@@

Because the importance of Gleason's theorem, its proof have been rewritten
to be more accessible~\cite{CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}.

>>>>

\begin{definition}[Quantum Probability Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
Given a Hilbert space $\Hilb$ with its set of events~$\events$,
a \emph{quantum probability measure} is a function~$\mu:\events\rightarrow[0,1]$
such that:\footnote{It is possible to define a more general space of events consisting
of all operators~$\mathcal{A}$ on $\Hilb$ and to extend $\mu$
linearly to $\mathcal{A}$ and consider $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$
is the expectation value of $A$ which could bigger than one because
$\mu$ is linear. We does not take this approach because we want to
focus only on probability. } 
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, 
\begin{equation}
\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)\textrm{ .}\label{eq:QuantumReal-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=0}^{N-1}$,
we have 
\begin{equation}
\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{N-1}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumReal-valuedProbability-Add}
\end{equation}
\end{itemize}
\qed\end{definition}

@@

Because the importance of Gleason's theorem, its proof have been rewritten
to be more accessible~\cite{CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
Since the additivity of the quantum probability measure~(\ref{eq:QuantumReal-valuedProbability-Add}),
a quantum probability measure~$\mu$ is completely determined by
its value on the one-dimensional projections~$\mu\left(\proj{\psi}\right)$.
